### 2016-03-15 paper/stereo.tex
yasu

We compare SF against competing approaches over three problems in
Computer Vision, namely, stereo, optical flow, and layered depthmap
estimation.

@@

\noindent For simple stereo problems with submodular energy as ours,
the sophistication of photometric consistency
function~\cite{mvs_furukawa_survey} makes unary terms highly
informative, where highly efficient algorithms such as graph-cuts
exist. Our experiments have also supported this, where the fusion
method (i.e., the use of proposal generation) rather makes it slow due
to the overhead, while not improving final energy. Therefore, we have
chosen algorithms based on Alpha-Expansion, namely single thread Alpha
Expansion(AE), Parallel Alpha
Expansion(PAE)~\cite{fusion_moves_for_markov_random_field_optimization}
and Hierarchical Fusion(HF)~\cite{olga_hierarchical_alpha_expansion}
to be competing methods. For HF, we use Alpha-Expansion when either of
the child node is leaf node (constant label) and QPBO for all other
nodes.

@@

\noindent The three swarm architectures in Fig.~\ref{fig:model} have
been evaluated: SF-MF (SF without multi-way fusion), SF-SS (SF without
solution sharing), and the standard SF.
%
SF-MF implies $\alpha+\beta=1$, where each thread will expand 4 labels
(repeat $\alpha=1, \beta=0$ for 4 iterations) with Alpha Expansion and
then fuse one solution from other threads ($\alpha=0, \beta=1$) by
QPBO. In the later case, a thread randomly chooses one solution from
the solution pool for fusion. SF-SS implies $\beta=0$, where $\alpha$
is the free parameter and set to 4. In this case one thread will fuse
4 labels, together with current solution by TRW-S per iteration and
never exchanges solutions with other threads. We perform a multi-way
fusion at the end to fuse solutions from all the threads (similar to
PAE). For standard SF, we have used ($\alpha=4, \beta=1$).

%
%
%
%
To make the comparison simple, we restrict our proposal generator
in each thread to only generate constant-label proposals within a
subset of all labels.
%
% Due to the lack of multi-way fusion, the swarm fusion architecture for
% the stereo problem is represented by the middle example at the bottom of
% Fig.~\ref{fig:model}.

>>>>

We compare SF against competing approaches over three problems in
Computer Vision, specifically, stereo, optical flow, and layered
depthmap estimation.

@@

\noindent For simple stereo problems with submodular energy as ours, the
sophistication of photometric consistency
function~\cite{mvs_furukawa_survey} makes unary terms highly
informative, where efficient inference algorithms such as graph-cuts
exist.
%Our experiments have also supported this, where the fusion method
%(i.e., the use of proposal generation) rather makes it slow due to the
%overhead, while not improving final energy.
Therefore, we have chosen algorithms based on Alpha-Expansion, namely
single thread Alpha Expansion(AE), Parallel Alpha
Expansion(PAE)~\cite{fusion_moves_for_markov_random_field_optimization}
and Hierarchical Fusion(HF)~\cite{olga_hierarchical_alpha_expansion} to
be competing methods. For HF, we use Alpha-Expansion at the leaf node of
the label tree or QPBO in the other cases.
%when either of the
%child node is leaf node (constant label) and QPBO for all other nodes.

@@

\noindent The three swarm architectures in Fig.~\ref{fig:model} have
been evaluated: SF-MF (SF without multi-way fusion), SF-SS (SF without
solution sharing), and the standard SF.
%
SF-MF implies $\alpha+\beta=1$, where each thread repeats
fusing a solution proposal ($\alpha=1, \beta=0$) for four iterations
by Graph-cuts and fusing a concurrent solution  ($\alpha=0, \beta=1$)
for one iteration by QPBO.
%expand 4 labels (repeat $\alpha=1, \beta=0$ for 4 iterations) with Alpha
%Expansion and then fuse one solution from other threads ($\alpha=0,
%\beta=1$) by QPBO.
In the later case, a thread randomly chooses one solution from the
solution pool for fusion. SF-SS implies $\beta=0$, where $\alpha$ is the
free parameter and set to 4. In this case one thread will fuse 4 labels,
together with current solution by TRW-S per iteration and never
exchanges solutions with other threads. We perform a multi-way fusion
of solutions from all the threads at the end to obtain a final solution
% at
% the end to fuse solutions from all the threads to a single solution
(similar to PAE). For standard SF, we have used ($\alpha=4, \beta=1$).
%
%
%
%
To make the comparison simple, we restrict our solution proposals
to be constant-label proposals.
%
% Due to the lack of multi-way fusion, the swarm fusion architecture for
% the stereo problem is represented by the middle example at the bottom of
% Fig.~\ref{fig:model}.
